Optimizing Abstract Abstract Machines

### 2012-11-14 paper/paper.tex
Yes it is David: on this planet, bigger is better.
Added comments on what might be unsettling at first glance about the graphs.

Figure~\ref{fig:bench-overview} gives an overview of the benchmark
results in terms of absolute time, space, and speed between the
baseline and most optimized analyzer.  Figure~\ref{fig:bench-all}
plots the factors of improvement over the baseline for each
optimization step.

@@

  (c) Total analysis time
\end{center}
\caption{Factors of improvement over baseline for each step of
  optimization.}
\label{fig:bench-all}
\end{figure*}

>>>>

Figure~\ref{fig:bench-overview} gives an overview of the benchmark
results in terms of absolute time, space, and speed between the
baseline and most optimized analyzer.  Figure~\ref{fig:bench-all}
plots the factors of improvement over the baseline for each
optimization step. The dip we see in transition rate even though time
taken decreases is to be expected - fewer ``easy'' states are added by
abstract compilation. It increases again with the introduced
algorithmic improvements. Accumulating store changes in addition to
maintaining the store accounts for the higher memory usage when using
the store delta technique without further improvements.

@@

  (c) Total analysis time
\end{center}
\caption{Factors of improvement over baseline for each step of
  optimization (bigger is better).}
\label{fig:bench-all}
\end{figure*}
